\thispagestyle{plain}
\chapter*{\Huge Acknowledgements}
First and foremost, I want to thank Prof. Bernt Schiele for
supervising my thesis, and being a constant source of inspiration and
motivation throughout the time. In particular, I am grateful for his
confidence in my abilities from the beginning, which allowed me to
grow from a layman in computer vision to being fluent in object class
recognition.
Likewise, I thank Prof. Michael Goesele for
co-supervising my thesis and agreeing to serve as an examiner. I am
more than thankful for his advice, which often proved invaluable, precisely
because of its non-vision perspective.
I am truly grateful to Prof. Martial Hebert for serving as an
external reviewer as part of the thesis committee.

I would also like to express my gratitude to all members of the MIS,
IU, ESS, and GRIS groups, not only for supporting me with inspiring
discussions and feedback concerning research, but also sharing a lot
of fun moments in leisure activities: Jens Ackermann, Anton Andriyenko, Eugen Berlin,
Ulf Blanke, Marko Borazio, Victoria Carlsson, Dr. Gyuri Dorko, Simon
Fuhrmann, Dr. Tam Huynh,
Nikodem Majer, Kevin Schelten, Paul Schnitzspan, Dr. Edgar Seemann,
Dr. Ulrich Steinhoff, Christoph Vogel,
Stefan Walk, Dr. Maja Stikic, and Dr. Andreas Zinnen. I owe particular
thanks to Ursula
Paeckel, for being the good soul of the group, and having a
sympathetic ear for all matters, and my office mates Dr. Christian Wojek
and Micha Andriluka for many fruitful discussions and out of line
thinking. I thank Dr. Mario Fritz and Dr. Kristof van Laerhoven for
sharing both their expertise and sense of humor, and Dr. Diane Larlus
for saving my life in Kyoto with her Japanese.

Furthermore, I would like to thank my collaborators, without whom I
would not have had the chance to complete this thesis:
Prof. Iryna Gurevych,
Philipp Lies,
Marcus Rohrbach,
Prof. Konrad Schindler,
Dr. Gy{\"o}rgy Szarvas,
Dr. Jeremy Wyatt,
Dr. Michael Zillich,
and Zeeshan Zia. Similarly, my thanks go to the students that I had
the opportunity to supervise and work with, Sebastian Schneider and
Sandra Ebert.

I further thank the EU project CoSy and the DFG for providing both
funding and an exciting context for my research, and allowing me to
collaborate with many great researchers around the globe.

Lastly, I am very grateful to many people that encouraged me to
continue my way in research, especially Dr. Patrick Lehti, Dr. Peter
Fankhauser, Dr. Mary F. Fern{\'a}ndez, and Dr. J{\'e}r{\^o}me
Sim{\'e}on. Most of all, I thank my family, in particular my parents,
and my dear friends Gerald Bork and Wolfgang Lennartz for always
believing in me, and pulling me back onto the ground in testing times.
\begin{itemize}
%\item ICCV07: This work has been funded, in part, by the EU project
%  CoSy (IST-2002-004250). The authors would like to thank A. Berg and
%  V. Ferrari for providing implementations of \GB and \kAS,
%  respectively, T. Kadir, D. Lowe and K. Mikolajczyk for making their
%  feature implementations available to the community, and C. Wojek for
%  joint boosting code.
%\item ICVS08: This work has been funded, in part, by the EU project
%  CoSy (IST-2002-004250).
%\item ICCV09: This work has been funded, in part, by EU project CoSy
%  (IST-2002-004250), and DFG Emmy Noether grant GO1752/3-1.\\
\item CVPR 12: We would like to thank Ulf Blanke for code and discussions on activity recognition.
\item TACL 13: We'd like to thank Asad Sayeed, Alexis Palmer and Prashant Rao for their help with the annotations.  We're indebted to Carl Vondrick and Marco Antonio Valenzuela Escárcega for their extensive support with the video annotation tool. Further we thank Alexis Palmer and in particular three anonymous reviewers for their helpful comments on this paper. -- This work was funded by the Cluster of Excellence ``Multimodal Computing and Interaction'' of the German Excellence Initiative and the DFG project SCHI989/2-2.
\item CVPR10: The authors would like to thank Torsten Zesch for
 providing the ESA measure index for Wikipedia \citep{zesch09jnle},
 Giuseppe Pirr{\`o} for the Java WordNet Similarity Library
 \citep{pirro08odbase}, and Yahoo for the BOSS API.
 \item eccv 10: The authors would like to thank Torsten Zesch for providing the ESA measure index for Wikipedia \cite{zesch09jnle}, Giuseppe Pirr{\`o} for the Java WordNet Similarity Library \cite{pirro08odbase}, and Yahoo for the BOSS API.\textsuperscript{\ref{fn:publish}}
\end{itemize}

% LocalWords:  ICCV
