\pagestyle{empty}
\definecolor{light}{gray}{0.65}
%
%%\section*{{\textcolor{light}{\Huge \bf Curriculum Vitae}}}
%\section*{{\Huge \bf Publications}}
%%\addcontentsline{toc}{chapter}{\protect\numberline{}{Curriculum Vitae}}   %% see book p. 176
%\vspace{0.02\textwidth}

\chapter*{\Huge{Publications}}
{[12]} \textit{Transfer Learning in a Transductive Setting.}\\ 
\ul{Marcus Rohrbach}, Sandra Ebert, and Bernt Schiele. \\
In Advances in Neural Information Processing Systems 26 (\textbf{NIPS}), 2013.
\\
\\
{[11]} \textit{Translating video content to natural language descriptions.}\\
\ul{Marcus Rohrbach}, Wei Qiu, Ivan Titov, Stefan Thater, Manfred Pinkal, and Bernt Schiele.\\ 
In International Conference on Computer Vision (\textbf{ICCV}), 2013. 
\\
\\
{[10]} \textit{Multi-view Pictorial Structures for 3D Human Pose Estimation.}\\ 
Sikandar Amin, Mykhaylo Andriluka, \ul{Marcus Rohrbach}, and Bernt Schiele.\\ 
In British Machine Vision Conference (\textbf{BMVC}) 2013.
\\
\\
{[9]} \textit{Grounding Action Descriptions in Videos.} \\
Michaela Regneri, \ul{Marcus Rohrbach}, Dominikus Wetzel, Stefan Thater, Bernt Schiele, and Manfred Pinkal.\\ 
Transactions of the Association for Computational Linguistics (\textbf{TACL}), 1:25--36, 2013.
\\
\\
{[8]} \textit{Script data for attribute-based recognition of composite activities.}\\
\ul{Marcus Rohrbach}, Michaela Regneri, Mykhaylo Andriluka, Sikandar Amin, Manfred Pinkal, and Bernt Schiele.\\
Computer Vision - \textbf{ECCV} 2012 : 12th European Conference on Computer Vision, 2012.
\\
\\
{[7]} \textit{3D object detection with multiple kinects.}\\
Wandi Susanto, \ul{Marcus Rohrbach}, and Bernt Schiele.  \\
Computer Vision - \textbf{ECCV} 2012 : Workshops and Demon-strations, volume 7584 of Lecture Notes in Computer Science, 2012.
\\
\\
{[6]} \textit{A database for fine grained activity detection of cooking activities.}\\
\ul{Marcus Rohrbach}, Sikandar Amin, Mykhaylo Andriluka, and Bernt Schiele.\\
In 2012 IEEE Conference on Computer Vision and Pattern Recognition (\textbf{CVPR}), 2012.
\\
\\
{[5]} \textit{Evaluating Knowledge Transfer and Zero-Shot Learning in a Large-Scale Setting.}\\
\ul{Marcus Rohrbach}, Michael Stark, and Bernt Schiele.\\  
In 2011 IEEE Conference on Computer Vision and Pattern Recognition (\textbf{CVPR}), 2011.
\\
\\\newpage
\noindent{[4]} \textit{The Benefits of Dense Stereo for Pedestrian Detection.}\\
Christoph G. Keller, Markus Enzweiler, \ul{Marcus Rohrbach}, David Fern{\'a}ndez and Llorca, Christoph Schn{\"o}rr, and Dariu M. Gavrila.\\
IEEE Transactions on Intelligent Transportation Systems (\textbf{TITS}), 12:1096--1106,2011.
\\
\\
{[3]} \textit{Combining Language Sources and Robust Semantic Relatedness for Attribute-Based Knowledge Transfer.} \\
\ul{Marcus Rohrbach}, Michael Stark, Gy{\"o}rgy Szarvas, Bernt Schiele.\\
In First International Workshop on Parts and Attributes ({\bf PnA2010}), in
conjunction with {\bf ECCV} 2010, published in Trends and
Topics in Computer Vision : ECCV 2010 Workshops, Volume 6553 of Lecture Notes in Computer Science, 2012.
\\
\\
{[2]} \textit{"What Helps Where {\textendash} And Why? Semantic Relatedness for Knowledge Transfer."} \\
\ul{Marcus Rohrbach}, Gy{\"o}rgy Szarvas, Iryna Gurevych, Bernt Schiele.\\
In IEEE Conference on Computer Vision and Pattern Recognition ({\bf CVPR}), 2010.
\\
\\
{[1]} \textit{High-level fusion of depth and intensity for pedestrian classification.}\\
\ul{Marcus Rohrbach}, Markus Enzweiler, and Dariu M. Gavrila.\\
In Proceedings of the 31st DAGM Symposium on Pattern Recognition (\textbf{DAGM}), 2009.